---
title: "data-wrangle"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loadpackages}
library(minpack.lm)
library(ggplot2)
library(tidyverse)
library(knitr)
library(Stat2Data)
library(growthcurver)
library(epifitter)
library(nlstools)
library(nlsMicrobio)
library(easynls)
library(numDeriv)
```

```{r import-data}
library(readxl)
trmb_data <- read_excel("~/Desktop/data+/20181214_trmB_all_data.xlsx")
trmb_meta <- read_excel("~/Desktop/data+/20181214_meta_trmB_all.xlsx")
```

trmb_data and trmb_meta are the two original data files. Each variable number in trmb_data corresponds to one value in trmb_meta. The following data wrangling code combines the two graphs and outputs a single more straightforward dataset for data analysis and visualizations. Ideally, trmb_data and trmb_meta can be any experimental data with any number of independent variables as long as the experiment has three technical and biological replicates.

```{r rearrangement-and-indexing}
trmb_rearranged <- trmb_meta %>%
  drop_na(name) %>%
  group_by(condition, media, name, biorep, techrep, variable) %>%
  count()

trmb_rearranged <- trmb_rearranged %>%
  select(!n)

trmb_rearranged$index <- 1:nrow(trmb_rearranged)

sorted_by_variable <- trmb_rearranged %>%
  mutate(variable = as.numeric(variable)) %>%
  arrange(variable)

trmb_sorted_merge <- sorted_by_variable %>%
  group_by(variable, index) %>%
  select(variable, index)
```

```{r changed-name}
trmb_rearranged %>%
  group_by(condition, media, name) %>%
  count()

trmb_rearranged <- trmb_rearranged %>% 
  add_column(new_name = NA)

renamed_meta <- unite(trmb_rearranged, condition, media, name, 
                      col = "new_name", sep = "_")

#renamed_meta <- renamed_meta %>%
  #mutate(number = 3*biorep + techrep - 3)

renamed_meta <- renamed_meta %>%
  mutate(number = ifelse(is.na(biorep) == FALSE, 3*biorep + techrep -3, index))

renamed_meta <- unite(renamed_meta, new_name, number, 
                      col = "new_name", sep = "_")
```

```{r alter-data-file-for-merging}
trmb_flip <- as.data.frame(t(trmb_data))
index <- c(0)
index <- c(index, trmb_sorted_merge$index)
trmb_flip['index'] <- index

trmb_flip <- trmb_flip %>%
  arrange(index) %>%
  select (!index)

renamed <- c(0)
renamed <- c(renamed, renamed_meta$new_name)
trmb_flip['renamed'] <- renamed

trmb_df <- as.data.frame(t(trmb_flip))
```

```{r rename-column-for-meta}
new_col = c("Time")
new_col = c("Time", trmb_df[nrow(trmb_df), ][-1])
colnames(trmb_df) = new_col

n<-dim(trmb_df)[1]
trmb_df<-trmb_df[1:(n-1),]
```

```{r character-to-numeric}
trmb_df <- trmb_df %>% mutate_if(is.character,as.numeric)
```

```{r display}
trmb_df
```


```{r reorganize}
#control group - meta
renamed_meta_blank <- renamed_meta %>%
  filter(is.na(biorep))

#control group - data
trmb_data_blank <- trmb_df %>%
  select(Time, contains("blank"))

#experimental group - meta
renamed_meta_not_blank <- renamed_meta %>%
  filter(!is.na(biorep))

#experimental group - data
trmb_data_not_blank <- trmb_df %>%
  select(!contains("blank"))
```